\cvsection{Experience}

\cventry
  {Senior Data Engineer (Consultant to SageSure)}
  {ISHIR / SageSure}
  {Remote}
  {2024 -- 2026}
  {
    \begin{cvitems}
      \item {Owned Redshift-based analytics platform for US insurance, building scalable ELT pipelines (dbt, S3, Lambda) and API integrations for high-volume policy and claims data.}
      \item {Translated business initiatives into data assets and dimensional models, improving query performance and report delivery times for analytics teams.}
      \item {Implemented data validation suites and tests using data APIs, reducing data quality incidents and rework in downstream reports.}
      \item {Partnered with BI and product stakeholders to troubleshoot data issues, refine KPIs, and harden the semantic layer for self-service analytics.}
      \item {Recognized with Rising Star and Team Excellence awards for delivery quality and collaboration.}
    \end{cvitems}
  }

\cventry
  {Data Engineer}
  {CannaSpyglass}
  {Remote}
  {2021 -- 2023}
  {
    \begin{cvitems}
      \item {Built data pipelines for cannabis wholesalers, transporters, growers, dispensaries, and Google Maps data across AWS and GCP.}
      \item {Scraped and ingested PDFs, spreadsheets, and e-commerce sources using Scrapy, Requests, and Selenium on EC2, Glue, and Lambda, landing curated datasets in RDS and S3.}
      \item {Automated data quality checks and troubleshooting workflows, ensuring reliable inputs for BI dashboards and regulatory reporting.}
      \item {Collaborated with analytics teams to enhance BI tools and create reusable data assets for market and operational insights.}
    \end{cvitems}
  }

\cventry
  {Data Scientist}
  {AI Squared}
  {Remote}
  {2020 -- 2021}
  {
    \begin{cvitems}
      \item {Developed Java Spring Boot APIs and statistical models for a COVID-19 risk assessment platform used by over 2M users.}
      \item {Created Java bindings for R packages, enabling production-grade statistical workflows and predictive models.}
      \item {Designed data funneling strategies on AWS (EC2, Glue, S3, Athena, Lambda, RDS) to support advanced analytics and reporting.}
      \item {Worked closely with stakeholders to define KPIs, run deep-dive analysis, and recommend improvements across multiple projects.}
    \end{cvitems}
  }

\cventry
  {Assistant Project Manager}
  {Casepoint}
  {India}
  {2018 -- 2019}
  {
    \begin{cvitems}
      \item {Managed and delivered data-heavy projects over \$1M revenue, coordinating with US-based senior stakeholders.}
      \item {Designed data strategies including pipeline design and SQL/NoSQL data stores to support legal analytics and reporting.}
      \item {Automated reporting and analysis with Excel macros, improving turnaround time and reducing manual effort.}
      \item {Drove Agile/Scrum ceremonies, tracked risks, and implemented mitigation plans for data processing workflows.}
    \end{cvitems}
  }
